Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-16 paper/paper.tex
finish discussion section

\subsection*{Goal}
This article proposes a machine listening system which computes the dissimilarity in timbre between any two audio samples.
Our system consists of two stages: unsupervised feature extraction and supervised metric learning.
The feature extraction stage is a nonlinear map which relies on the joint time--frequency scattering transform \cite{anden2015mlsp,anden2019tsp}, followed by per-feature Gaussianization \cite{lostanlen2018jasmp}.
It encodes patterns of spectrotemporal modulation in the query while offering numerical guarantees of stability to local deformations.
The metric learning stage is a linear map, optimized via large-margin nearest neighbors (LMNN) \cite{weinberger2009distance}.
It recombines scattering coefficients so as to fit a training set of human judgments \cite{mcadams1995psychres}, which may either stem from the perceptual idiosyncracies of a single subject or from a collective consensus.

>>>>

\subsection*{Goal}
This article proposes a machine listening system which computes the dissimilarity in timbre between any two audio samples.
Our system consists of two stages: unsupervised feature extraction and supervised metric learning.
The feature extraction stage is a nonlinear map which relies on the joint time--frequency scattering transform \cite{anden2015mlsp}, followed by per-feature Gaussianization \cite{lostanlen2018jasmp}.
It encodes patterns of spectrotemporal modulation in the query while offering numerical guarantees of stability to local deformations.
The metric learning stage is a linear map, optimized via large-margin nearest neighbors (LMNN) \cite{weinberger2009distance}.
It recombines scattering coefficients so as to fit a training set of human judgments \cite{mcadams1995psychres}, which may either stem from the perceptual idiosyncracies of a single subject or from a collective consensus.
